---
title: "Exercise #3"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Chanyoung Woo (12368781)"
date: "`r Sys.Date()`"
output: distill::distill_article
editor_options: 
  markdown: 
    wrap: 72
---

## General Remarks

-   You can submit your solutions in teams of up to 3 students.
-   Include all your team-member's names and student numbers
    (Martrikelnummern) in the `authors` field.
-   Please use the exercise template document to work on and submit your
    results.
-   Use a level 2 heading for each new exercise and answer each subtask
    next to it's bullet point or use a new level 3 heading if you want.
-   Always render the R code for your solutions and make sure to include
    the resulting data in your rendered document.
    -   Make sure to not print more than 10 rows of data (unless
        specifically instructed to).
-   Always submit both the rendered document(s) as well as your source
    Rmarkdown document. Submit the files separately on moodle, **not**
    as a zip archive.

## Exercise 1: Initializing git (4 Points)

For this whole exercise sheet we will be tracking all our changes to it
in git.

a)  Start by initializing a new R project with git support, called
    `2024-exeRcise-sheet-3`. If you forgot how to do this, you can
    follow this
    [guide](https://malikaihle.github.io/Introduction-RStudio-Git-GitHub/rstudio_project.html).

-done

b)  Commit the files generated by Rstudio.

-done

c)  For all of the following tasks in this exercise sheet we ask you to
    always commit your changes after finishing each subtask e.g. create
    a commit after task *1d*, *1e* etc.

> Note: This applies only to answers that have text or code as their
> answer. If you complete tasks in a different order or forget to commit
> one, this is no problem. If you change your answers you can just
> create multiple commits to track the changes.

-done

d)  Name 2 strengths and 2 weaknesses of git. (Don't forget to create a
    commit after this answer, see *1c*)

**2 strengths of Git:** - Every git user has access to all the versions
of the ongoing git-project. This enables offline work and efficient
version management. - Also one of the greatest strength of git is
Branching and Merging. This allows users to work on multiple development
paths and merging it afterwards. You don't have to wait for someone to
finish working so you can work on the project. You can just create
different branches and merge it afterwards.

**2 weaknesses of Git:** - The extensive set of Git-commands are very
complex and difficult for beginners. So for beginners there are many
things to learn before even to get started with git. - Also for
beginners problems/conflicts can be difficult to solve. Especially
Merging conflicts in large projects can be very challenging to resolve.

e)  Knit this exercise sheet. Some new files will automatically be
    generated when knitting the sheet e.g. the HTML page. Ignore these
    files, as we only want to track the source files themselves.

## Exercise 2: Putting your Repository on GitHub (3.5 Points)

For this task you will upload your solution to GitHub.

a)  Create a new repository on GitHub in your account named
    `exeRcise-sheet-3`. Make sure you create a **public repository** so
    we are able to see it for grading. Add the link to the repository
    below:

<https://github.com/Reiskorn03/exeRcise-sheet-3>

b)  Push your code to this new repository by copying and executing the
    snippet on github listed under
    `…or push an existing repository from the command line`.

-done

c)  Regularly push your latest changes to GitHub again and especially do
    so when you are finished with this sheet.

-done

## Exercise 3: Baby-Names in Munich (3.5 Points)

Download the latest open datasets on given names ("Vornamen") from the
open data repository of the city of Munich for the years `2023` and
`2022`.

Link: <https://opendata.muenchen.de/dataset/vornamen-von-neugeborenen>

a)  Download the data for both years and track it in git. For small
    datasets like these adding them to git is not a problem.

-done

b)  Load the data for both years into R. Check the type of the count
    variable ("Anzahl") and look into the data to determine why it is
    not numeric? Fix the problem in an appropriate manner, it is OK if
    some of the counts are inaccurate because of this. Explain your
    solution and the repercussions.

```{r 3b, echo = TRUE}
library(dplyr)
data_2023 <- read.csv("vornamen-muenchen-2023.csv")
data_2022 <- read.csv("open_data_portal_2022.csv")

str(data_2023)
str(data_2022)
summary(data_2023)
summary(data_2022)

class(data_2023$Anzahl)
class(data_2022$Anzahl)

data_2023$Anzahl <- gsub("4 oder weniger", "2", data_2023$Anzahl)
data_2022$Anzahl <- gsub("4 oder weniger", "2", data_2022$Anzahl)

data_2023$Anzahl <- as.numeric(gsub("[^0-9]", "", data_2023$Anzahl))
data_2022$Anzahl <- as.numeric(gsub("[^0-9]", "", data_2022$Anzahl))

summary(data_2023$Anzahl)
summary(data_2022$Anzahl)
```

Why are some of the values in **"Anzahl"** not numeric? **Answer:** As
in further inspection of the two .csv files, if the count variable
"Anzahl" is less than or equals to 4, it automatically defines its value
to "4 oder weniger" which is translated to "smaller or equals 4". So
this is the reason why non-numeric values are defined as values of the
count variables. **Solution:** To fix this issue of non-numeric values
in the count variable, I changed all non-numeric values to 2, because 2
is the median of [0, 1, 2, 3, 4]. This may lead to a
over/underestimation of the count variable that are actually more/less
than 2. Also this data set may be distorted because now there are many
values that equals 2, but it does not matter because the data set was
inaccurate in the first place.

c)  Calculate the total number of babies born in Munich in 2022
    and 2023. Which year had the bigger baby-boom?

```{r 3c, echo = TRUE}
total_babies_2022 <- sum(data_2022$Anzahl)
total_babies_2023 <- sum(data_2023$Anzahl)

cat("Total number of babies born in 2022:", total_babies_2022, "\n")
cat("Total number of babies born in 2023:", total_babies_2023, "\n")

if (total_babies_2023 > total_babies_2022) {
  cat("2023 had the bigger baby-boom.\n")
} else if (total_babies_2023 < total_babies_2022) {
  cat("2022 had the bigger baby-boom.\n")
} else {
  cat("Both years had the same number of babies born.\n")
}
```

d)  Add a new column `year` to both datasets which holds the correct
    year for each.

```{r 3d, echo = TRUE}
data_2022$year <- 2022
data_2023$year <- 2023

head(data_2022)
head(data_2023)
```

e)  Combine both datasets into one using `bind_rows()`.

```{r 3e, echo = TRUE}
combined_data <- bind_rows(data_2022, data_2023)

str(combined_data)
summary(combined_data)
```

f)  Combine the counts for same names to determine the most popular
    names across both years. Print out the top 10 names in a nicely
    formatted table for both years. Include a table caption.

```{r 3f, echo = TRUE}
name_counts <- combined_data %>%
  group_by(Vorname, Geschlecht) %>%
  summarise(Total = sum(Anzahl, na.rm = TRUE)) %>%
  arrange(desc(Total))

top_10_names <- head(name_counts, 10)

knitr::kable(
  top_10_names, 
  caption = "Top 10 Most Popular Baby Names in Munich (2022 and 2023)")
```

## Exercise 4: Open Analysis (4 points)

This exercise is a bit more open-ended. You can choose any dataset from
[Our World in Data](https://ourworldindata.org/) and analyze it, while
determining the research question yourself.

a)  Go to <https://github.com/owid/owid-datasets/tree/master/datasets>
    and choose a dataset that interests you. You can have a look at
    <https://ourworldindata.org/> to gather some inspiration.

Smoking prevalence and cigarette consumption (IHME, GHDx (2012)).csv

b)  Download the dataset and track it in git.

-done

c)  Put the name / title of the dataset and a link to it below.

-   Dataset Name: Smoking prevalence and cigarette consumption (IHME,
    GHDx (2012)).csv
-   Link:
    [https://github.com/owid/owid-datasets/blob/master/datasets/Smoking%20prevalence%20
    and%20cigarette%20consumption%20(IHME%2C%20GHDx%20(2012))/Smoking%20prevalence
    %20and%20cigarette%20consumption%20(IHME%2C%20GHDx%20(2012)).csv]
    (https://github.com/owid/owid-datasets/blob/master/datasets/Smoking%20prevalence
    %20and%20cigarette%20consumption%20(IHME%2C%20GHDx%20(2012))/Smoking%20prevalence
    %20and%20cigarette%20consumption%20(IHME%2C%20GHDx%20(2012)).csv){.uri}

d)  Come up with a (research) question you want to answer with the data
    and briefly explain why you believe this is an interesting question
    within one sentence. It should be a question that can be answered
    with the dataset and using R.

**Question:** Which 3 countries have the highest cigarette consumption per smoker per day in 2010?
**Explanation:** It is really interesting which of the countries have the highest cigarette consumption per smoker per day because with this information you can possibly track how many cigarettes the country is consuming with the amount of smokers in their country.

e)  Use R to answer your chosen question.

```{r 4e, echo = TRUE}
library(dplyr)
library(ggplot2)
library(readr)

cigarette_data <- 
  read_csv(
    "Smoking prevalence and cigarette consumption (IHME, GHDx (2012)).csv", 
           show_col_types = FALSE)

data_2010 <- cigarette_data %>%
  filter(Year == 2010)

data_2010 <- data_2010 %>%
  dplyr::select(
    Entity, 
    Year, 
    `Cigarette consumption per smoker per day (IHME, GHDx (2012))`)

colnames(data_2010)[3] <- "Cigarettes_per_day"

top_3_countries <- data_2010 %>%
  arrange(desc(Cigarettes_per_day)) %>%
  head(3)

knitr::kable(
  top_3_countries, 
  caption = "Top 3 Countries with Highest 
  Cigarette Consumption per Smoker per Day in 2010")
```

f)  Create a meaningful plot / figure with the dataset. Make sure to
    provide a figure caption (via the chunk options / Rmarkdown) and
    correctly label the figure.

```{r 4f, echo = TRUE}
library(dplyr)
library(ggplot2)
library(readr)

cigarette_data <- 
  read_csv("Smoking prevalence and cigarette consumption (IHME, GHDx (2012)).csv", 
           show_col_types = FALSE)

germany_data <- cigarette_data %>%
  filter(Entity == "Germany") %>%
  dplyr::select(Year, `Cigarette consumption per smoker per day (IHME, GHDx (2012))`)

colnames(germany_data)[2] <- "Cigarettes_per_day"

ggplot(germany_data, aes(x = Year, y = Cigarettes_per_day)) +
  geom_line(color = "blue") +
  geom_point(color = "red") +
  labs(title = "Trend of Cigarette Consumption per Smoker per Day in Germany",
       x = "Year",
       y = "Cigarettes per Day") +
  theme_minimal()
```

## Final Note

Make sure to push all your commits and changes to GitHub before
submittining the exercise sheet.


